Aggressive Scheduling for Numerical Programs

### 2012-05-02 report/draft.tex
added

In order to enforce a schedule at the C code level we need to prevent the
compiler from imposing its own scheduling. A compiler must preserve the
semantics of the input code, so to take advantage of this fact we place a
label before each instruction with a \emph{goto} nested in
a \emph{switch-case} block. We declare the value for the \emph{switch}
statement as a global variable set such that the code will always jump to the
first instruction. Initially, we simply embedded each instruction in
a \emph{switch-case} block, but both the GCC and Intel compiler would create
multiple code paths and schedule each path individually. Figure~\ref{} shows
an example of our method in practice.

@@

>>>>

In order to enforce a schedule at the C code level we need to prevent the
compiler from imposing its own scheduling. A compiler must preserve the
semantics of the input code, so to take advantage of this fact we place a
label before each instruction with a \emph{goto} nested in
a \emph{switch-case} block. We declare the value for the \emph{switch}
statement as a global variable set such that the code will always jump to the
first instruction. Initially, we simply embedded each instruction in
a \emph{switch-case} block, but both the GCC and Intel compiler would create
multiple code paths and schedule each path individually. Fig.~\ref{fig:force_sched} shows
an example of our method in practice.

@@

\begin{figure}[ht]
\begin{lstlisting}
int state=0;

void test(double  *Y, double  *X) {
    switch(state) {
      case 1: {
      goto label1;        }
      case 2: {
      goto label2;        }
      /* .... snip .... */
      case 26: {
      goto label26;        }
      case 27: {
      goto label27;        }
    }

    label1:
    a91 = (X + 1);
    label2:
    a95 = *(X);
    /* .... snip .... */
    label26:
    a111 = *(a94);
    label27:
    a112 = (Y + 3);
}

\end{lstlisting}
\caption{A template for enforcing an instruction ordering in C.}
\label{fig:force_sched}
\end{figure}
